# Armadillo Mapper (v0.1.0)

Armadillo Mapper (AM) is a web application that automatically updates the potential distribution of the hairy long-nosed armadillo (*Dasypus pilosus*), which is endemic to the cloud forest and subparamo habitats of Peru. Users could upload new observations of *D. pilosus* and AM will output the updated potential distribution made by [Maxent algorithm](version 3.3.3k; https://biodiversityinformatics.amnh.org/open_source/maxent/).



There are three ways to use AM.

1. User can direct use AM via this [link](http://armadillomapper.fengxiao.info).

2. User can download this repository and deploy it on a Shiny server [(see more instructions)](https://shiny.rstudio.com/deploy/).

3. If user wants to run AM locally (e.g., a personal Rstudio).

i) AM requires the following R packages *leaflet*, *shiny*, *dismo*, *raster*, *sp*, *rJava*, and *ggplot2* to be installed.
```{r, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
install.packages(c("leaflet","shiny","dismo","raster","sp","ggplot2","rgeos","rJava"))
```
AM relies on Maxent algorithm, thus user must put a copy of **maxent.jar** [(download)](https://github.com/mrmaxent/Maxent/tree/master/ArchivedReleases/3.3.3k) in a specific folder. Put the file 'maxent.jar' in the 'java' folder of *dismo* package. The folder can found by running **system.file("java", package="dismo")**. Additional, R and Java must both be under  32-bit or 64-bit (e.g., 32-bit R & 32-bit Java). Please refer to more details of runing maxent in R by running **?dismo::maxent**

```{r}
library("leaflet")
library("shiny")
library("dismo")
library("raster")
library("sp")
library("ggplot2")
library("rgeos")
library("rJava")
runGitHub("ArmadilloMapper", "shandongfx")
```



# More details of the source code

AM mainly relies on two R scripts: one draws the user interface and the other one implements the spatial analysis, model training, and distribution prediction on a server. The data analysis and map display rely on several R packages: dismo, raster, sp , and leaflet. 


