---
title: "title"
author: Xiao Feng
date: June 27, 2017
output: md_document
---

# Armadillo Mapper (v0.1.0)

Armadillo Mapper (AM) is a web application that automatically updates the potential distribution of the hairy long-nosed armadillo (*Dasypus pilosus*), which is endemic to the cloud forest and subparamo habitats of Peru. Users could upload new observations of *D. pilosus* and AM will output the updated potential distribution made by [Maxent algorithm](version 3.3.3k; https://biodiversityinformatics.amnh.org/open_source/maxent/).



There are three ways to use AM.

1. User can direct use AM via this [link](http://armadillomapper.fengxiao.info).

2. User can download this repository and deploy it on a Shiny server [(see more instructions)](https://shiny.rstudio.com/deploy/).

3. If user wants to run AM locally (e.g., a personal Rstudio).

i) AM requires the following R packages *leaflet*, *shiny*, *dismo*, *raster*, *sp*, *rJava*, and *ggplot2* to be installed.
```{r, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
install.packages(c("leaflet","shiny","dismo","raster","sp","ggplot2","rgeos","rJava"))
```
ii) AM relies on Maxent algorithm, thus user must put a copy of **maxent.jar** [(download)](https://github.com/mrmaxent/Maxent/tree/master/ArchivedReleases/3.3.3k) in a specific folder. Put the file 'maxent.jar' in the 'java' folder of *dismo* package. The folder can found by running **system.file("java", package="dismo")**. Additional, R and Java must both be under  32-bit or 64-bit (e.g., 32-bit R & 32-bit Java). Please refer to more details of runing maxent in R by **?dismo::maxent**

```{r, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library("leaflet")
library("shiny")
library("dismo")
library("raster")
library("sp")
library("ggplot2")
library("rgeos")
library("rJava")
runGitHub("ArmadilloMapper", "shandongfx")
```


## Overview of functions of folders and files  
ArmadilloMapper/  
├── ui.R                `draws the interface`  
├── server.R            `implements all analysis`  
├── global.R            `defines languages & colors`    
├── raw_data_clean/     `stores data of Feng et al. (2017)`    
├── raw_data_clean/web translation_v2.csv  `stores strings of the interface (English/Spanish)`    
├── www/  `stores html elements`    
├── www/google-analytics.js  `Google Analytics script`    
├── maxent_outputs/  `stores maxent output`    
└── userUpload/  `stores user uploaded data`    
